Joint maximum-likelihood of phylogenies and ancestral states is not consistent

### 2018-03-02 joint_inf.tex
MBE submission requirements
Adding B cell grant.

\documentclass{article}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{showlabels}
\usepackage{palatino}
\usepackage{hyphenat}
\usepackage{thm-restate}
\usepackage{lineno}
\linenumbers
\usepackage{natbib}
\usepackage{setspace}
\doublespacing
\usepackage{authblk}
\usepackage{fancyhdr}

@@

This work was supported by National Institutes of Health grants R01-AI12096, U19-AI117891, and U54-GM111274 as well as National Science Foundation grants CISE-1561334 and CISE-1564137.
The research of Frederick Matsen was supported in part by a Faculty Scholar grant from the Howard Hughes Medical Institute and the Simons Foundation.

>>>>

\documentclass[11pt]{article}

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{showlabels}
\usepackage{palatino}
\usepackage{hyphenat}
\usepackage{thm-restate}
\usepackage{lineno}
\linenumbers
\usepackage{natbib}
\usepackage{setspace}
\onehalfspacing
\usepackage{authblk}
\usepackage{fancyhdr}

@@

This work was supported by National Institutes of Health grants R01-GM113246, R01-AI12096, U19-AI117891, and U54-GM111274 as well as National Science Foundation grants CISE-1561334 and CISE-1564137.
The research of Frederick Matsen was supported in part by a Faculty Scholar grant from the Howard Hughes Medical Institute and the Simons Foundation.
